Dependent Object Types

### 2012-08-08 article.tex
subset sem lemma

The subset semantics lemma states that if (1) $v \in \relv k \Gamma s S$
and (2) $\Gamma \ts S <: U$, then $v \in \relv k \Gamma s U$.

\begin{proofsketch}
Because $S$ is a subtype of $U$, it should hold that the expansion of
$S$ subsumes the expansion of $U$. Therefore, for $v \in \relv k
\Gamma s U$, we have fewer and ``simpler'' definitions to check than
for $v \in \relv k \Gamma s S$. One worry is that for methods, because
the parameter type is contravariant, $U$ could require a more precise
type than $S$. This shouldn't lead to narrowing issues, because if the
parameter type becomes ill-typed, then the check is vacuously true.
\end{proofsketch}

>>>>

The subset semantics lemma states that if $v \in \relv k \Gamma s S$
and $\Gamma \ts S <: U$, then $v \in \relv k \Gamma s U$.

\begin{proofsketch}
Because $S$ is a subtype of $U$, it should hold that the expansion of
$S$ subsumes the expansion of $U$. Therefore, for $v \in \relv k
\Gamma s U$, we have fewer and ``simpler'' definitions to check than
for $v \in \relv k \Gamma s S$. One worry is potential narrowing
issues for methods: because the parameter type is contravariant, $U$
can require a more precise type than $S$. This should be fine, because
if the parameter type becomes ill-typed, then the check is vacuously
true.
\end{proofsketch}
